---
title: "extension gallery config information"
format: html
editor: visual
---

## 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tidyverse.quiet = TRUE)
```

```{r}
library(tidyverse)
```

## 

We want to look at the packages submitted to the ggplot2 extension gallery at <https://exts.ggplot2.tidyverse.org/gallery/.>

To add an ggplot2 extension, there is this instruction

> Add an entry for your extension in the \_config.yml file of this repository with the meta data for your extension (copy another entry and modify). Please see below for guidance on the meta data.

```{r, eval = F}
 read_lines("https://raw.githubusercontent.com/ggplot2-exts/gallery/refs/heads/gh-pages/_config.yml") |> 
  write_lines("ext_config_yml.txt")
```

Here is one of the entries.

```{r}
read_lines("ext_config_yml.txt")[8:23]
```

Maybe we can easily collect all this info if we remove the returns before indentations... (the description fields)

```{r}
read_lines("ext_config_yml.txt") |>
  paste(collapse = "\n") |>
  str_replace_all("\\>\n    ", "") |>
  str_replace_all("\n    ", "") |>
  str_split("\n") |>
  _[[1]] ->
config_initial_parse

config_initial_parse |> head(20)

```

```{r}
config_initial_parse |>
  tibble(config_text = _) |>
  separate(config_text, sep = ": ", into = c("item", "content")) %>% 
  filter(!is.na(content)) %>% 
  mutate(name = ifelse(item == "- name", content, NA)) %>% 
  select(name, everything()) %>% 
  mutate(item = str_trim(item)) %>% 
  fill(name) %>% 
  filter(!is.na(name)) %>% 
  filter(item != "- name") %>% 
  pivot_wider(names_from = item, values_from = content) ->
config_dataframe

head(config_dataframe)
```

```{r}
write.csv(config_dataframe, "gallery_config.csv")
```
