---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# ggplot2-extension-ecosystem

<!-- badges: start -->
<!-- badges: end -->

The ggplot2-extension-ecosystem [github repo](https://github.com/EvaMaeRey/ggplot2-extension-ecosystem) will help us work on the 'Who are the ggplot2 extenders? and how to become one'.

Abstract idea:

The intuitiveness and power of ggplot2 (2007) has led to massive popularity, and has been a boon in domains like scientific investigation, business informatics, and education.  Base capabilities are extensive, and allow users to fluidly build and customize many charts.   The existence of ggplot2 extension mechanisms and an ecosystem of extension developers and packages means that plotting in domains that base ggplot2 doesn't handle can also be created within the familiar and powerful ggplot2 framework.  This paper attempts to characterize the ecosystem, especially focusing on extenders and pathways for individuals to enter the extension space. 

Panel abstract:

Since its release, ggplot2 (Wickham 2007) has become a widely used tool for data visualization. Based on the "grammar of graphics" (Wilkinson 1999), ggplot2 provides a flexible framework for creating highly customizable graphics. In addition, as Wickham and coauthors put it, "the ggplot2 package ... makes it relatively easy to extend the functionality with new types of the common grammar components" (https://ggplot2-book.org/extensions). Consequently, the ggplot2 ecosystem now includes hundreds of extension packages that add new functionality via the prescribed extension mechanisms (e.g. themes, stats, geoms, and scales) as well as those that introduce variations in dialect into the grammar, tailored to domain-specific needs. This panel brings together developers for a lively exchange of ideas, from broad questions about the landscape as a whole to technical ones on extension package internals. The session will include ample time for discussion between audience members and the panelists.

 
Here links to html rendered files:

```{r, results = 'asis', echo = F}
library(magrittr)
webpages <- fs::dir_ls(type = "file", 
                       recurse = T, 
                       glob = "*.html|*.pdf") %>% 
  rev()

file_name_wo_extension <- webpages %>% 
  stringr::str_remove(".html|.pdf")
 
webpages %>%    
  paste0("1. [",
         . ,
         "]",
         "(https://evamaerey.github.io/ggplot2-extension-ecosystem/", ., 
         ") **[source](https://github.com/evamaerey/ggplot2-extension-ecosystem/blob/master/",
         file_name_wo_extension,".qmd",
         ")**\n") %>% 
  cat()     
```


And to tabular data...

```{r, results = 'asis', echo = F}
library(magrittr)
webpages <- fs::dir_ls(type = "file", 
                       recurse = T, 
                       glob = "*.csv") %>% 
  rev()



file_name_wo_extension <- webpages %>% 
  stringr::str_remove(".csv")
 
webpages %>%    
  paste0("1. [",
         . ,
         "]",
         "(https://github.com/EvaMaeRey/ggplot2-extension-ecosystem/blob/main/", ., ")\n") %>% 
  cat()     



```
